Self Regulation Ontology Retest Analyses

### 2018-07-24 code/SRO_Retest_Analyses.Rmd
replacing stats

tmp %>%
  ggplot(aes(similarity, value, col=key))+
  geom_smooth(method="lm", se=FALSE)

summary(lm(value~key*similarity,tmp))
```

>>>>

tmp %>%
  ggplot(aes(similarity, value, col=key))+
  geom_smooth(method="lm", alpha = 0.15)+
  ylab("Polychoric correlation")+
  xlab("Levenshtein distance")+
  scale_color_discrete(breaks = c("t1_t1_polycor", "t2_t2_polycor"),
                       labels = c("T1 correlations", "T2 correlations"),
                       name = element_blank())+
  theme_bw()

ggsave('OverlappingItemSimilarity.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
```

```{r}
summary(lm(value~key*similarity,tmp))
effect.size(lm(value~key*similarity,tmp))
```

```{r}
summary(MCMCglmm(value ~ key*similarity, data=tmp, nitt = 50000)) 
```
